---
title: "Perl WC Jan 11 2021"
output: html_notebook
---

## 95

1. Palindrome number detector

> Are first & last digits the same?

* Read them off in pairs, shelling each pair as you go, until there are no more pairs.
* This will work for odd & even numbers.

> Does converting to other bases help?

> Convert to string?

* They are symmetric about a (possibly missing) central element.

> Is there a geometric representation?

*Much* easier way. Calculate the mid point, slice the digits to the left and string compare with right!

Easier still - convert to string - reverse - compare!!!!


```{r}
library(tidyverse)
n1 <- 11
n2 <- 111
n3 <- 1111

pldrm_detect <- function(.n){
  
  n.as.str <- .n %>% as.character()
  str.as.n <- n.as.str %>% str_split('') %>% unlist() %>% rev() %>% str_c(collapse = '')
  n.as.str == str.as.n
}


c(n1,n2,n3,122) %>% map_lgl(~{
  pldrm_detect(.x)
  })

```

Could build a classifier?
Somehow get from 121,true, 122,false training set to 'reverse & test equality'

Numeric method - split digits into halves - lhs == rhs.

Simply involves masking.

* Detect power of 10
* Calculate 1/2 way, e.g if power of 10 == 3 1/2 way = 2
* Create mask to take left-most (or right-most) digits e.g. '111000' for the first 3 powers of a 6 digit number.
* original - masked 
  + Leaves either the right or leftmost digits.
* Reverse to get the other side
* Compare

```{r}
  po10 <- function(.x,.o=0){
    .x.next <- .x/10
    (.x.next < 1) && return(.o)
    po10(.x.next,.o+1)
  }

pldrm_detect2 <- function(.n){
  # Detect power of 10
  p <- po10(.n)
  p
}

c(1,11,111) %>% map_dbl(pldrm_detect2)

```


> Is there a probabilistic interpretation?

> How would you design a function to generate a palidrome?

> Is there something about 11's?

Using a 'digirator' ($digi$ts ite$rator$) a reasonably simple method is:

1. For each iteration multiply the digit by the power that is the reverse of its power in the original sequence - e.g no matter how many digits there are the last digit will be the first digit * $10^0$.
2. Add the result to the running total of summed digits-to-the-reverse-power.
3. You have your reversed digit sequence for comparison with the original.

```{r}

make_digirator <- function(.n){
  
  n.digits <- log10(.n) %>% floor()
  tmp.n <- .n
  function(){
    if(n.digits == -1){ return(NULL)}
    
    next.d <- ( tmp.n/(10^n.digits)) %>% floor()
    #glimpse(tibble(power = n.digits, n = tmp.n,d = next.d))
    tmp.n <<- tmp.n - next.d*10^n.digits ## Note 'look up' assignment
    n.digits <<- n.digits-1 ## Note 'look up' assignment
    next.d
  }
  
}

test_digirator <- function(){
digirate_22 <- make_digirator(22)

digirate_22()
digirate_22()

digirate_127 <- make_digirator(127)

digirate_127()
digirate_127()
digirate_127()
digirate_127()
}

digi_mirror <- function(.n){

  n <- abs(.n)
  p_or_ng <- .n/n
  digrater <- make_digirator(n)
  n.digits <- log10(n) %>% ceiling()
  n.revd <- 0
  d.i <- 0
  while (!is.null(d <- digrater()) ) {
    expt <- d.i
    n.revd <- n.revd + d*(10^expt)
    d.i <- d.i+1
  }
  n.revd*p_or_ng
}

is_palindrome <- function(.n){
  
  .n == digi_mirror(.n)
  
}

is_palindrome(11)
is_palindrome(12)
is_palindrome(1221)
is_palindrome(12021)
is_palindrome(12210)
is_palindrome(-11)
is_palindrome(-110)
```


There is a way to reverse 2 & 3 digit numbers if you know the 1st & last digits -
For 2 digit numbers subtract the 2nd from 1st, multiply the result by 9, and subtract from starting number.
e.g 27
$$
27 \\
2-7 = -5  \\
-5*9 = -45 \\
27 - - 45 = 72 \\
\\
53 \\
5-3 = 2 \\
2*9 = 18 \\
53-18 = 35
$$

For 3 digit numbers multiply by 99 instead of 9.

For digit counts > 3 this method will only work if the middle digts are the same (obviously). But it does suggest a general method, here described for an even number of digits:

1. Split the number into successive digit pairs, $p1,p2,...$ using the 'power-mask' method ($\copyright$ LRNOP) e.g with 274106:
  + 27 41 06
2. For each pair use the method of 9's
  + 72 14 60
3. Reverse the sequence of pairs
  + 60 14 72
4. Ta da.

```{r}
## Monster the digirator to make it return tuples
make_n_digirator <- function(.n,.t.size=1){
  
  n.digits <- log10(.n) %>% ceiling()
  n.tups <- (n.digits/.t.size) %>% ceiling()
  tup.count <- 0

  tmp.n <- .n
  function(){
    if(n.tups == tup.count){ 
      ##Reset the counters in case the iterator is to be re-used
        tmp.n <<- .n
        n.digits <<- log10(.n) %>% ceiling()
        #n.tups <<- n.digits/.t.size
        tup.count <<- 0
        print('DONE')
      return(NULL)
    }
    power <- n.digits-.t.size
    next.tup <- ( tmp.n/(10^power)) %>% floor()
    # glimpse(tibble(power = power
    #                , n = tmp.n
    #                ,tup = next.tup
    #                ,tup.sz=.t.size
    #                ,total.digits=n.digits
    #                ,odd.parity = odd.parity )
    #         )
    tmp.n <<- tmp.n - next.tup*10^power ## Note 'look up' assignment
    n.digits <<- power ## Note 'look up' assignment
    #n.tups <<- n.tups-1
    tup.count <<- tup.count+1
    next.tup
  }
  
}

test_n_drtr <- function(){
  drtr <- make_n_digirator(1234,.t.size=1)
  while(!is.null(d <- drtr())){
    (d)
  }
}
test_n_drtr()

n1 <- 123456
n2 <- 123321

n_drtr <- make_n_digirator(1234,.t.size=2)
while(!is.null(d <- n_drtr())){
    print(d)
  }

1:2 %>% map_dbl(~{n_drtr()})

## Need to handle odd numbers
n_drtr2 <- make_n_digirator(12345,.t.size=2)
while(!is.null(d <- n_drtr2())){
    print(d)
  }

1:3 %>% map_dbl(~{n_drtr2()})

n_drtr3 <- make_n_digirator(1234567,.t.size=2)

while(!is.null(d <- n_drtr3())){
    print(d)
  }

1:4 %>% map_dbl(~{n_drtr3()})


```

2. Stack ops

eg.

push($n) - add $n to the stack
pop() - remove the top element
top() - get the top element
min() - return the minimum element

```{r}

```

